\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Appendix D: Acceptable Use Policy}
\subsection{Overview and Purpose}
\begin{enumerate}
    \item The purpose of this policy is to establish acceptable and unacceptable use of data, information, network resources, and electronic devices at \CompanyName{} in conjunction
    with a culture of ethical and lawful behavior, openness, trust, and integrity that allow \CompanyName{} to remain competitive in a crowded market.
    \item \CompanyName{} provides computer devices, networks, and other electronic information systems and access to information and services to meet \CompanyName{} goals, initiatives,
    and to serve clients and stakeholders. \CompanyName{} must manage its information systems and assets responsibly to maintain confidentiality, integrity, and availability of its assets
    and information. Users granted access to \CompanyName{} assets must then serve as stewards of those assets and comply with applicable policies.
\end{enumerate}
\subsection{Scope}
This policy applies to entities and assets as outlined in the Cybersecurity and IT Policy base document.
\subsection{Enforcement}
See enforcement clause in the Cybersecurity and IT Policy.
\subsection{Roles and Responsibilities}
This policy inherits Roles and Responsibility from the Cybersecurity and IT Policy in the base policy document.
\subsection{Acronyms and Definitions}
\begin{enumerate}
    \item Honeypot, Honeynet - technical infrastructure that serve as early-warning systems.
    \item Spam - Electronic junk mail or junk newsgroup postings. Messages that are unsolicited, unwanted, and irrelevant.
\end{enumerate}
\subsection{Policy}
\begin{enumerate}
    \item General Requirements
    \begin{enumerate}
        \item \CompanyName{} proprietary information stored on devices, whether owned or leased by you, \CompanyName, or a third-party, remains the sole property of \CompanyName.
        \CompanyName{} personnel may access, use, or share \CompanyName{} proprietary information only to the extent it is authorized and necessary to fulfill their assigned job duties.
        \item You are responsible for exercising good judgement regarding appropriate use of \CompanyName{} resources in accordance with all \CompanyName{} policies, standards, and guidelines.
        \CompanyName{} resources shall never be used for any unlawful or prohibited purpose.
        \item You shall not take any action that hinders, reduces, or otherwise interferes with \CompanyName's ability to go to market and win. You shall not negatively impact
        the \CompanyName's confidentiality, integrity, or availability of and or to assets without proper authorization from the correct authorities at the \CompanyName.
        For questions about which specific people or committees may authorize such an action, see \CompanyName's legal department and \CompanyName{} leadership.
        \item For security, compliance, and maintenance purposes, \CompanyName{} may authorize personnel or assets to monitor and audit all infrastructure, user accounts, and systems per
        the IT and Cybersecurity Policy. Often, these include network and endpoint scanning. To achieve a high-degree of success and inventory of current vulnerabilities, approved audit
        leaders may disconnect or temporarily disable systems, such as various forms of firewalls, that prevent scans. Users may not actively block authorized audits or scans.
    \end{enumerate}
    \item Accounts, Passwords, and Credentials
    \begin{enumerate}
        \item You are responsible for and the steward of all data, information, user accounts, technical infrastructure, and computers systems under your control and or custodial responsibility.
        \item All accounts or the equivalent of an account will be protected by a username, and password, and multifactor authentication when applicable and available.
        As technology changes and \CompanyName{} implements that same technology this clause may have exceptions.
        \item You will protect all accounts or access with strong passwords that meet the following criteria:
        \begin{enumerate}
            \item Must be 20 or more characters long.
            \item Must contain at least one capital letters, one numbers, and one special character
        \end{enumerate}
        \item Passwords will not be stored unencrypted at any time and should be stored within one of the \CompanyName's approved password managers provided here:
        \begin{enumerate}
            \item PasswordManager using an official \CompanyName{} email address
        \end{enumerate}
        \item In addition to a password, users shall protect accounts or access with an additional factor using a \CompanyName{} approved multi-factor authentication tool. You are allowed to use either of the following tools with a mobile phone and your \CompanyName{} accounts:
        \begin{enumerate}
            \item Google Authenticator
            \item Authy
            \item Azure Authenticator
        \end{enumerate}
        \item SMS (text messages) are NOT approved for use with \CompanyName-associated accounts that have multi-factor authentication as an option. Services that do not offer multi-factor
        authentication or are forcing SMS should be reported to and tracked by the security team.
        \item We recommend using a backup phone, when possible, to save your MFA seeds to reduce impact following a lost or stolen device.
        \item User accounts and accesses, including passwords, will not be shared with anyone at any time including the IT team, badged personnel, third party stakeholder, family, or friends.
        Doing so, regardless of the reason, is a violation of this policy. Exceptions must be documented in the Exceptions register.
        \item In some cases, a shared account may be authorized to co-manage services that do not support identity access management or role-based controls. In such cases,
        the shared account must be approved by the CISO and documented by the IT Team. Credentials for all such shared accounts will be stored in the approved password manager in such a way that
        the IT Team can enforce and monitor role-based access of the shared credentials.
        \item Change default and initial passwords and other credentials as soon as you acquire them. This is non-negotiable.
        \item Should an account, access, credential, or password ever be compromised or disclosed, that credential must be immediately changed unless otherwise approved by the
        security team who is authorized to weigh the costs and benefits associated with the high-risk alternative.
        \item You must ensure through legal and or technical means that proprietary information and critical data—especially PII and payment card data—always remain within the \CompanyName's control.
        \item Conducting \CompanyName{} business that results in the storage of proprietary information on personal or non-\CompanyName{} controlled environments,
        including devices maintained by a third-party with whom \CompanyName{} does not have a contractual agreement is prohibited. This specifically prohibits the use of an email account that is not
        provided by \CompanyName{} or its customers and partners for \CompanyName{} business.
    \end{enumerate}
    \item Computing Assets
    \begin{enumerate}
        \item You are responsible for ensuring the protection of assigned \CompanyName{} assets that includes the use of computer cable locks and other security devices.
        Laptops and desktops left at \CompanyName{} overnight will be secured by a locked door or with a cable lock at a minimum. When possible, laptops and other portable devices will be stored
        in a locked drawer or cabinet.
        \item Promptly report any theft or loss of \CompanyName{} assets to the Facilities Manager and to the IT team.
        \item All PCs, PDAs, laptops, workstations, or computing equipment must be secured with an automatic lockout after 10 minutes or less. You must lock your computer or log off when your
        device is unattended.
        \item Devices that connect to the \CompanyName{} network must comply with the IT and Cybersecurity Policy.
        \item Do not interfere with \CompanyName's device management or security systems or software, including but not limited to:
        \begin{enumerate}
            \item List of \CompanyName{} tools
            \item Remote Management tools
            \item EDR tools
            \item MDM tools
            \item Other tools
        \end{enumerate}
        \item When traveling with \CompanyName{} devices, devices are NOT to be left unattended. Specifically, you are not allowed to leave \CompanyName{} devices in any vehicle.
        The highest probability of loss of a device is when YOU leave it in a car while you go to dinner. This is not acceptable.
        \item When at home, devices must be kept in a separate location with the ability to limit physical access by other people in the household.
        A locked bedroom door or desk drawer are acceptable.
    \end{enumerate}
    \item Asset Use
    \begin{enumerate}
        \item You are responsible for the security and appropriate use of \CompanyName{} network resources under your control. Using any \CompanyName{} resources for the following is strictly prohibited:
        \begin{enumerate}
            \item Disclosing \CompanyName{} intellectual property or controlled information.
            \item Causing a security breach to \CompanyName{} assets which you are not authorized, circumventing user authentication on any device, or capture network traffic.
            \item Causing a disruption of service to either \CompanyName{} or any other network resources including but not limited to ARP cache poisoning, DoS/DDoS, etc.
            \item Accessing \CompanyName{} assets for any purpose other than conducting \CompanyName{} business.
            \item Introducing any technology, equipment, or data to the \CompanyName{} network or platforms without approval from the IT Team.
            \item Hosting, copying, or using unlicensed content or software or any content in a way that violates the intellectual property rights of another entity.
            \item Exporting or importing anything that would violate any applicable export control laws.
            \item Use of the internet or \CompanyName{} network that violates the IT and Cybersecurity Policy, \CompanyName{} policies, or local laws.
            \item Intentionally introducing malicious code.
            \item Conducting any offensive or defensive cybersecurity actions that you are not specifically authorized to do and only when windows that you are authorized to do them.
        \end{enumerate}
        \item Termination of Access
        \begin{enumerate}
            \item The IT or Information Security Team will revoke terminated users' access to \CompanyName{} assets and accounts immediately upon the effective date of terminated employment, contract, or agreement regardless of whether the termination was voluntary or involuntary except when legal hold, investigation, or other conditions necessitate. During such exceptions, the user’s access will be terminated but the account and data will be maintained unchanged.
            \item Terminated access applies to both individual accounts and any approved, shared accounts.
            \item \CompanyName{} may terminate access for employees in other situations as required.
        \end{enumerate}
        \item Electronic Communications
        \begin{enumerate}
            \item The following are strictly prohibited:
            \begin{enumerate}
                \item Inappropriate use of any \CompanyName{} asset to conduct any illegal or criminal activity or transmit any communication that violates the Employee Handbook.
                Examples include disclosing intellectual property, harassing anyone, or breaking laws.
                \item Fraud: Making fraudulent offers or forging, misrepresenting, obscuring, suppressing, or replacing a user identity on any electronic communication to mislead the recipient
                about the sender.
                \item Making statements about warranty, expressly or implied, unless it is part of normal business duties assigned.
                \item Posting the same or similar non-business-related messages to large numbers of online forums, social media, public messaging groups, newsgroups.
                \item Use of a \CompanyName{} email or IP address to engage in conduct that violates \CompanyName{} policies or guidelines. Posting to a public forum, messaging service,
                social media account, newsgroup, bulletin board, or other messaging board with a \CompanyName{} email or IP address represents \CompanyName{} to the public; therefore, you must
                exercise good judgement to avoid misrepresenting or exceeding your authority to represent the opinion of \CompanyName—any social media post from a \CompanyName{} email address
                or IP address should contain a disclaimer stating that the opinions expressed are strictly their own and not necessarily those of \CompanyName{} unless posting in the course
                of business duties.
            \end{enumerate}
        \end{enumerate}
    \end{enumerate}
    \item Annual Training
    \begin{enumerate}
        \item All staff and employees must complete annual security trainings and participate in any simulations or exercises conducted by the information security or IT teams.
    \end{enumerate}
    \item Exceptions
    \begin{enumerate}
        \item Deviations from or exceptions from these policies shall be submitted to the CISO and IT Team for approval and documentation respectively.
    \end{enumerate}
    \item Agreement
    \newline
    By signing below, you indicate that you have read the above requirements and policies for acceptable use of \CompanyName{}  information systems and understand your responsibilities regarding the
    use of \CompanyName{}  systems and assets and the information contained in them.
\end{enumerate}

 ---------------------------------------------------------------------------------------------
\newline NAME: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\newline DEPARTMENT: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\newline SIGNATURE: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\newline DATE: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{document}