\documentclass[../main.tex]{subfiles}
\usepackage{enumitem}

\begin{document}
\section{Admin (164.308)}
    \subsection{Security Management Process}
        Implement policies and Implement policies and procedures to prevent, detect, contain, and correct security violations. \emph{Ref 164.308(a)(1)(i)}\cite{us}

        \subsubsection{Risk Analysis (required)}
            Conduct and accurate and thorough risk and vulnerability assessment evaluation CIA for PHI. \emph{rRef 164.308(a)(1)(ii)(A)}\cite{us}

            \vspace{3mm}

            \noindent As indicated in the IT and Cybersecurity Policy's Review and Risk Assessment Section, ECOM will conduct an annual risk assessment with its MSP

        \subsubsection{Risk Management (required)}
            Implement security measures sufficient to reduce risks and vulnerabilities to a reasonable and appropriate level to comply with 164.306(a). \emph{Ref 164.308(a)(1)(ii)(B)}\cite{us}

            \vspace{3mm}

            \noindent ECOM's IT and Cybersecurity Policies cover access controls, asset management, and vulnerability management

        \subsubsection{Sanction Policy (required)}
            Apply sanctions to workforce members who fail to comply with security policies and procedures. \emph{Ref 164.308(a)(1)(ii)(C)}\cite{us}

            \vspace{3mm}

            \noindent IT and Cybersecurity Policies require log review as part of Access Control Policy; ECOM will establish a log aggregation solution by the end of FY2022 and store 1 year of logs by the end of FY2023

        \subsubsection{Information System Activity Review (required)}
            Regularly review records of IT activity such as logs, access reports, and security incident tracking reports. \emph{Ref 164.308(a)(1)(ii)(D)}\cite{us}

            \vspace{3mm}

            \noindent ECOM leverages a vCISO to develop and maintain cybersecurity policy; SEE RACI CHART

    \subsection{Assign Security Responsibility}
        Identify the security official who is responsible for the development and implementation of policies and procedures. Ref 164.308(a)(2)\cite{us}

    \subsection{Workforce Security}
        Implement policies and procedures to ensure that all employees have appropriate access to PHI under 164.308(a)(4) and to prevent unauthorized access to PHI. \emph{Ref 164.308(a)(3)(i)}\cite{us}
        \subsubsection{Authorization and/or Supervision (addressable)}
            Implement procedures for the authorization and/or supervision of employees who work with PHI or where it might be access. \emph{Ref 164.308(a)(3)(ii)(A)}\cite{us}

            \vspace{3mm}

            \noindent IT and Cybersecurity policies control access to PHI based on role and department; IT implements groups and access based on department and supervisor needs.

        \subsubsection{Workforce clearance (addressable)}
            Determine that employees have appropriate access to PHI. \emph{Ref 164.308(a)(3)(ii)(B)}\cite{us}

            \vspace{3mm}

            \noindent IT and Cybersecurity policies control access to PHI and require periodic review of the principle of least privilege.

        \subsubsection{Termination Procedures (addressable)}
            Terminate access to PHI when the employee exits the organization or when applicable under 164.308(a)(3)(ii)(B) (3.B. above). \emph{Ref 164.308(a)(3)(ii)(C)}\cite{us}

            \vspace{3mm}

            \noindent Access control policy requires termination of all access to IT including ePHI on the day the employee is terminated.

    \subsection{Information access management}
        Implement access authorizing procedures for PHI consistent with 164.308(E). \emph{Ref 164.308(a)(4)(i)}\cite{us}

    \subsection{Security Awareness and training}
        Implement a security awareness and training program for all employees including management. \emph{Ref 164.308(a)(5)(i)}\cite{us}

    \subsection{Security Incident Procedures}
        Address security incidents. \emph{Ref 164.308(a)(6)(i)}\cite{us}

    \subsection{Contingency Plan}
        Establish and implement a plan to respond to emergencies (including natural disasters/hazards) that damage IT containing PHI. \emph{Ref 164.308(a)(7)(i)}\cite{us}

    \subsection{Evaluation}
        Perform periodic technical and nontechnical evaluation based on HIPAA rules when environments or operations change and affect the security of PHI. Establish the extent to which CE or BAs meet the administrative requirements of 164.308. \emph{Ref 164.308(a)(8)}\cite{us}

    \subsection{Business Associate contracts and other arrangements}
        Obtain assurances BAs will safeguard information IAW 164.314(a). CEs do not need to obtain assurances from sub-contractors. BAs do need assurances from sub-contractors. \emph{Ref 164.308(b)(1)-(2)}\cite{us}

\end{document}