\documentclass[../main.tex]{subfiles}
\usepackage{enumitem}

\begin{document}
\section{Appendix G: Security Awareness Policy and Program}
\subsection{Policy Statement}
This policy exists to drive stakeholder vigilance against incidents and motivate the team to report both potential and confirmed incidents.
\subsection{Purpose}
aWe win in the marketplace when we secure ourselves in the marketplace. That security requires us all users to strive to the collective goal of protecting our information and our assets.
\subsection{Scope}
\begin{enumerate}
    \item This policy applies to entities as outlined in the Cybersecurity and IT Policy base document.
    \item All \CompanyName{} users and external entities with access to \CompanyName{} information or information systems must receive training.
\end{enumerate}
\subsection{Policy}
\begin{enumerate}
    \item This policy is to educate users about risks to information and information systems and drive appropriate action at their privilege level.
    The \CompanyName{} security training and awareness program includes security awareness presentations, security reminders, general security training, system-specific security training,
    security management training and professional security education for members of the workforce. Additionally, our awareness and education program will include the following:
    \begin{enumerate}
        \item Annual mandatory training.
        \item Scheduled awareness surveys.
        \item Periodic unscheduled awareness assessments to assure compliance with the training.
        \item Feedback surveys to improve our awareness training and education program.
        \item Phishing campaigns.
        \item Social hacking campaigns.
        \item Live-person physical penetration tests.
        \item Special training for privileged account users and information custodians including but not limited to incident response training, incident response exercises,
        forensics training, government reporting, and chain of custody.
    \end{enumerate}
    \item When applicable, training completion and results will be maintained in the individuals Human Resources personnel file, as part of the permanent record.
\end{enumerate}
\subsection{Responsibility}
The CISO is responsible for this program, its direction, and its effectiveness with input from legal, HR, and the IT Committee.
\end{document}